### 2018-12-21 Sections/intro_to_QM.tex
Minor QM

The joint state vector of a multi-partite system is represented using a tensor\index{Tensor product} (or Kronecker) product Hilbert space, which has dimensionality equal to the product of their individual dimensions\footnote{This is in contrast to the dimensionality of composite classical systems, which grow additively.}, hence yielding the dreaded (cherished!) exponential growth in the complexity of quantum systems,
\begin{align}
\mathcal{H}_{A,B} = \mathcal{H}_A\otimes \mathcal{H}_B,	
\end{align}
where,
\begin{align}
\mathcal{H}_A &\in\mathbb{C}^M\,\,(\mathrm{system}\,A),\nonumber\\
\mathcal{H}_B &\in\mathbb{C}^N\,\,(\mathrm{system}\,B),\nonumber\\
\mathcal{H}_{A,B} &\in\mathbb{C}^{MN}\,\,(\mathrm{composite\,\,system}).	
\end{align}

@@

Importantly -- and this is a key feature of quantum mechanics -- we cannot control what the measurement outcome is. It occurs randomly\footnote{When we say `random' we really mean random, not quasi-random but actually deterministic. This true randomness is another of the unique and surprising features of quantum mechanics. Quantum mechanics is inherently and provably non-deterministic!} according to some classical probability distribution, given by the overlaps between the measurement projectors and the quantum state.

>>>>

The joint state vector of a multi-partite system is represented using a tensor\index{Tensor product} (or Kronecker) product Hilbert space, which has dimensionality equal to the product of their individual dimensions\footnote{This is in contrast to the dimensionality of composite classical systems, which grow additively.}, hence yielding the dreaded (cherished!) exponential growth in the complexity of quantum systems,
\begin{align}
\mathcal{H}_{A,B} = \mathcal{H}_A\otimes \mathcal{H}_B,	
\end{align}
where,
\begin{align}
\mathcal{H}_A &\in\mathbb{C}^M\,\,(\mathrm{system}\,A),\nonumber\\
\mathcal{H}_B &\in\mathbb{C}^N\,\,(\mathrm{system}\,B),\nonumber\\
\mathcal{H}_{A,B} = \mathcal{H}_A\otimes \mathcal{H}_B &\in\mathbb{C}^{MN}\,\,(\mathrm{composite\,\,system}).	
\end{align}

@@

Importantly -- and this is a key feature of quantum mechanics -- we cannot control what the measurement outcome is. It occurs randomly\footnote{When we say `random' we \textit{really} mean random, not quasi-random but actually deterministic. This true randomness is another of the unique and surprising features of quantum mechanics. Unlike classical physics, quantum mechanics is inherently and provably non-deterministic!\comment{Move this up to list}} according to some classical probability distribution, given by the overlaps between the measurement projectors and the measured quantum state.
